### 2016-05-12 text/Chapter03.tex
Fix references

Here, the variable context $\Gamma$ contains two variables, both of type \ident{Arr}. This means
$\Gamma = x\!:\!\ident{Arr},\, y\!:\!\ident{Arr}$. For simplicity, we treat \kvd{cursor} as a
language primitive. The coeffect annotations will be $(0,0)$ for $x$ and $(-1,1)$ for $y$,
denoting that we access only the current value in $x$, but we need access to both left and right
neighbours in the $y$ array. In order to unify the flat and structural notions, we attach this information
as a \emph{vector} of annotations associated with a \emph{vector} of variable and write:
$\coctx{x\!:\!\ident{Arr},\, y\!:\!\ident{Arr}}{ \aclrd{\alift{ (0,0), (-1,1) }} }$.
The unification is outlined in Section~\ref{ch:further-unified}.

@@

It is useful to clarify how vectors are used in this thesis. Suppose we have a set $\C$ of
\emph{scalars} ranged over by $\cclrd{r},\cclrd{s},\cclrd{t}$. A vector $\aclrd{R}$
over $\C$ is a tuple $\alift{ \cclrd{r_1}, \ldots, \cclrd{r_n} }$ of scalars.
We use bold face letters like $\aclrd{\textbf{r}}, \aclrd{\textbf{s}}, \aclrd{\textbf{t}}$ for
vectors and normal face $\cclrd{r},\cclrd{s},\cclrd{t}$ for scalars. We also say that a
\emph{shape} of a vector $\slen{\aclrd{\textbf{r}}}$ (or more generally any container)
determines the set of \emph{positions} in a vector. So, a vector of a shape (length) $n$ has positions
$\{ 1, 2, \ldots, n \}$. We discuss containers and shapes further in Section~\ref{ch:further-unified} and also
discuss how our use relates to containers of Abbott, Altenkirch and Ghani \cite{types-containers}.

@@

This chapter was divided into two major sections. First, we looked at \emph{flat} systems, which
track whole-context properties. Next, we look a \emph{structural} systems, which track per-variable
properties. Both of the variants are useful and important -- for example, implicit parameters can
only be expressed as \emph{flat} system, but liveness analysis is only useful as \emph{structural}.
For this reason, we explore both of these variants in this thesis (Chapter~\ref{ch:flat} and
Chapter~\ref{ch:structural}, respectively). We can, however, unify the two variants into a single
system discussed in Section~\ref{ch:further-unified}.

>>>>

Here, the variable context $\Gamma$ contains two variables, both of type \ident{Arr}. This means
$\Gamma = x\!:\!\ident{Arr},\, y\!:\!\ident{Arr}$. For simplicity, we treat \kvd{cursor} as a
language primitive. The coeffect annotations will be $(0,0)$ for $x$ and $(-1,1)$ for $y$,
denoting that we access only the current value in $x$, but we need access to both left and right
neighbours in the $y$ array. In order to unify the flat and structural notions, we attach this information
as a \emph{vector} of annotations associated with a \emph{vector} of variable and write:
$\coctx{x\!:\!\ident{Arr},\, y\!:\!\ident{Arr}}{ \aclrd{\alift{ (0,0), (-1,1) }} }$.
The unification is outlined in Section~\ref{sec:further-unified}.

@@

It is useful to clarify how vectors are used in this thesis. Suppose we have a set $\C$ of
\emph{scalars} ranged over by $\cclrd{r},\cclrd{s},\cclrd{t}$. A vector $\aclrd{R}$
over $\C$ is a tuple $\alift{ \cclrd{r_1}, \ldots, \cclrd{r_n} }$ of scalars.
We use bold face letters like $\aclrd{\textbf{r}}, \aclrd{\textbf{s}}, \aclrd{\textbf{t}}$ for
vectors and normal face $\cclrd{r},\cclrd{s},\cclrd{t}$ for scalars. We also say that a
\emph{shape} of a vector $\slen{\aclrd{\textbf{r}}}$ (or more generally any container)
determines the set of \emph{positions} in a vector. So, a vector of a shape (length) $n$ has positions
$\{ 1, 2, \ldots, n \}$. We discuss containers and shapes further in Section~\ref{sec:further-unified} and also
discuss how our use relates to containers of Abbott, Altenkirch and Ghani \cite{types-containers}.

@@

This chapter was divided into two major sections. First, we looked at \emph{flat} systems, which
track whole-context properties. Next, we look a \emph{structural} systems, which track per-variable
properties. Both of the variants are useful and important -- for example, implicit parameters can
only be expressed as \emph{flat} system, but liveness analysis is only useful as \emph{structural}.
For this reason, we explore both of these variants in this thesis (Chapter~\ref{ch:flat} and
Chapter~\ref{ch:structural}, respectively). We can, however, unify the two variants into a single
system discussed in Section~\ref{sec:further-unified}.

### 2016-05-12 text/Chapter04.tex
Context-aware systems edits (Chapter 3)
Fix references

In the previous chapter, we outlined a number of systems that capture how computations
access the environment in which they are executed. We identified two kinds of systems --
\emph{flat systems} capturing whole-context properties and \emph{structural systems} capturing
per-variable properties. As we show in Section~\ref{sec:unified-unified}, the systems can be
further unified using a single abstraction, but such abstraction is \emph{less powerful} -- \ie~its
generality hides useful properties that we can see when we consider the systems separately. For
this reason, we discuss \emph{flat coeffects} (Chapter~\ref{ch:flat} and Chapter~\ref{ch:semantics})
and \emph{structural coeffects} (Chapter~\ref{ch:structural}) separately.

@@

\item The idempotent monoid $(\C, \cpar, \czero)$ represents \emph{pointwise} composition,
\ie~the case when the same context is passed to multiple (independent) computations. The monoid
axioms guarantee that usual syntactic transformations on tuples and the unit value
(Section~\ref{sec:flat-exts}) preserve the coeffect. Idempotence holds for all our examples
and allows us to unify the flat and structural systems in Chapter~\ref{ch:unified}.

@@

\subsection{Understanding flat coeffects}
\label{sec:flat-calculus-undestanding}

@@

% ==================================================================================================
%
%     #####
%    #     #  ####  #    #  ####  #      #    #  ####  #  ####  #    #  ####
%    #       #    # ##   # #    # #      #    # #      # #    # ##   # #
%    #       #    # # #  # #      #      #    #  ####  # #    # # #  #  ####
%    #       #    # #  # # #      #      #    #      # # #    # #  # #      #
%    #     # #    # #   ## #    # #      #    # #    # # #    # #   ## #    #
%     #####   ####  #    #  ####  ######  ####   ####  #  ####  #    #  ####
%
% ==================================================================================================
\section{Conclusions}

>>>>

In the previous chapter, we outlined a number of systems that capture how computations
access the environment in which they are executed. We identified two kinds of systems --
\emph{flat systems} capturing whole-context properties and \emph{structural systems} capturing
per-variable properties. As we show in Section~\ref{sec:further-unified}, the systems can be
further unified using a single abstraction, but such abstraction is \emph{less powerful} -- \ie~its
generality hides useful properties that we can see when we consider the systems separately. For
this reason, we discuss \emph{flat coeffects} (Chapter~\ref{ch:flat} and Chapter~\ref{ch:semantics})
and \emph{structural coeffects} (Chapter~\ref{ch:structural}) separately.

@@

\item The idempotent monoid $(\C, \cpar, \czero)$ represents \emph{pointwise} composition,
\ie~the case when the same context is passed to multiple (independent) computations. The monoid
axioms guarantee that usual syntactic transformations on tuples and the unit value
(Section~\ref{sec:flat-exts}) preserve the coeffect. Idempotence holds for all our examples
and allows us to unify the flat and structural systems in Section~\ref{sec:further-unified}.

@@

%---------------------------------------------------------------------------------------------------
s
\subsection{Understanding flat coeffects}
\label{sec:flat-calculus-understanding}

@@

% ==================================================================================================
%
%     #####
%    #     #  ####  #    #  ####  #      #    #  ####  #  ####  #    #  ####
%    #       #    # ##   # #    # #      #    # #      # #    # ##   # #
%    #       #    # # #  # #      #      #    #  ####  # #    # # #  #  ####
%    #       #    # #  # # #      #      #    #      # # #    # #  # #      #
%    #     # #    # #   ## #    # #      #    # #    # # #    # #   ## #    #
%     #####   ####  #    #  ####  ######  ####   ####  #  ####  #    #  ####
%
% ==================================================================================================
\section{Summary}

### 2016-05-12 text/Chapter06.tex
Fix references

Our structural coeffect systems annotate the whole variable context with a \emph{vector} of annotations.
For example, a context with variables $x$ and $y$ annotated with $\cclrd{s}$ and $\cclrd{t}$,
respectively is written as $\coctx{x\!:\!\tau_1,y\!:\!\tau_2}{\alift{\cclrd{s},\cclrd{t}}}$.
A benefit of this approach is that the typing judgements have the same structure as those of the
flat coeffect calculus. As discussed in Chapter~\ref{ch:unified}, this makes it possible to unify
the two systems.

@@

\noindent
The fact that the tensor product $\atimes_{\sclrd{n},\sclrd{m}}$ is indexed by the lengths
of the two vectors means that we can use it unambiguously for both concatenation of vectors
and for splitting of vectors, provided that the lengths of the resulting vectors are known.
In the following text, we usually omit the indices and write just
$\aclrd{\textbf{r}} \atimes \aclrd{\textbf{s}}$, because the lengths of the coeffect vectors
can be determined from the lengths of the matching free variable context vectors.
More generally, we could see the the coeffect annotations as \emph{containers}
\cite{types-containers}. This approach is used in Chapter~\ref{ch:unified} to unify flat
and structural systems.

>>>>

Our structural coeffect systems annotate the whole variable context with a \emph{vector} of annotations.
For example, a context with variables $x$ and $y$ annotated with $\cclrd{s}$ and $\cclrd{t}$,
respectively is written as $\coctx{x\!:\!\tau_1,y\!:\!\tau_2}{\alift{\cclrd{s},\cclrd{t}}}$.
A benefit of this approach is that the typing judgements have the same structure as those of the
flat coeffect calculus. As discussed in Section~\ref{sec:further-unified}, this makes it possible to unify
the two systems.

@@

\noindent
The fact that the tensor product $\atimes_{\sclrd{n},\sclrd{m}}$ is indexed by the lengths
of the two vectors means that we can use it unambiguously for both concatenation of vectors
and for splitting of vectors, provided that the lengths of the resulting vectors are known.
In the following text, we usually omit the indices and write just
$\aclrd{\textbf{r}} \atimes \aclrd{\textbf{s}}$, because the lengths of the coeffect vectors
can be determined from the lengths of the matching free variable context vectors.
More generally, we could see the the coeffect annotations as \emph{containers}
\cite{types-containers}. This approach is used in Section~\ref{sec:further-unified} to unify flat
and structural systems.
